Pillar 1 - Sequential Pattern Mining

### 2019-02-05 Pillar 1 - Sequential Pattern Mining.Rmd
name chunks

The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
```{r my_apriori function}

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r function clean AR}

@@

```{r}
compute_support <- function(AR, data_support, type_rule){

@@

```{r}
make_AR <- function(data, appearance = NULL,
                    data_support, type_rule){

@@

```{r AR apriori, cache = TRUE}

>>>>

The function `my_apriori()` applies the apriori algorithm on a set of transactions with the parameters that we have chosen.
```{r my_apriori}

@@

The function `clean_AR()` transforms the rules generated by the function `my_apriori()` into a readable dataframe
```{r clean_AR}

@@

```{r compute_support}
compute_support <- function(AR, data_support, type_rule){

@@

```{r make_AR}
make_AR <- function(data, appearance = NULL,
                    data_support, type_rule){

@@

```{r AR, cache = TRUE}
